\section{Message from the General Chair}\vspace{2em}
\setheaders%
    {Message from the General Chair}%
    {Message from the General Chair}
\thispagestyle{emptyheader}
\setlength{\parskip}{1ex}
\setlength{\parindent}{0pt}

Welcome to the 2024 meeting of the North American Association for Computational Linguistics! This year, the conference is in Mexico City. NAACL was actually already planned for Mexico City in 2021, but due to the pandemic the entire conference was moved online. This year, finally, we get to go! So it is my sincere pleasure to welcome you to Mexico City, whether in person or virtually. Having the conference in Mexico City is a good opportunity to emphasize that NAACL is our flagship conference for ACL members not only in North America but also in Central and South America, even though NAACL  has been bearing ``North'' in its name. At this year's conference, we have a theme to match, with a theme track on the \textit{Languages of Latin America} to showcase the linguistic diversity of the region.

This year, we decided, along with EACL and ACL, to rely fully on ACL Rolling Review (ARR) for conference submissions. It has been exciting and impressive to see, up close, the amount of work that went into making the process run smoothly. Many thanks to the ARR editors in chief, in particular Thamar Solorio and Mausam, for developing innovations for the reviewing process to keep pace with our growing community. Many thanks to the program chairs of all three conferences, for dealing with all the detail troubles as they arose. A big thank you also to the OpenReview team, in particular Andrew McCallum, Melissa Bok and Harold Rubio, for adding improvements to the platform specifically for ACL and for working tirelessly with us to handle whatever came up. And an extra big thank you to Ryan Cotterell, who has been building the software that we use to publish from ARR and who worked with the OpenReview team to design the platform improvements, and to the ACL board, in particular Iryna Gurevych, for putting money into making OpenReview/ARR publishing better.

The opportunity to present at NAACL should not depend on a researcher's travel budget, or their family status. This is why it is so important to make virtual participation at NAACL as good an experience as possible -- but we want to also provide a good experience for in-person participants. As a community, we are still working out the best way to do that. This year at NAACL, we are trying out a big virtual poster session ahead of the conference, with the hope that this will make make for a lively and interactive experience. At the same time, we are reducing virtual oral presentations, which seem to be particularly tricky to make to work well. A big thanks to the NAACL program chairs and to Luciana Benotti for all their ideas and work to improve the virtual experience. And participants, virtual as well as in-person: Please let us know what worked for you and what didn't, so we can continue to
improve hybrid conferences. 

I have been lucky to work with many amazing people. Without their insight, dedication and patience, and without the many hours of work they put in, NAACL would not have been possible. A huge thank you to the program chairs Helena Gomez, Kevin Duh, and Steve Bethard -- you are the best!

And special thanks to  Jenn Rachford, the ACL business manager, who has dealt with room assignments, local arrangements in Mexico City, and so many details of conference planning. We couldn't have done it without your support and guidance.

And many thanks also to\ldots
\begin{itemize}
\setlength\parskip{0em}
\setlength\itemsep{0.3em}
\item The workshop chairs Niranjan Balasubramanian, Malihe Alikhani, and Alexis Palmer
\item The tutorial chairs Rui Zhang, Nathan Schneider and Snigdha Chaturvedi
\item The demo chairs Nazneen Rajani, Kai-Wei Chang and Annie Lee 
\item The industry track chairs Avi Sil, Yi Yang, Anoop Kumar, and Aida Davani 
\item The student workshop chairs Trista Cao, Isabel Papadimitriou and Anaelia Ovalle, and their faculty advisors Marcos Zampieri, Frank Ferraro and Swabha Swayamdipta
\item The publication chairs Ryan Cotterell, Maarten Sap and Lifu Huang
\item The website chairs Vered Shwartz and Xinya Du
\item The publicity and social media chairs Ximena Gutierrez-Vasques, Samuel Gonz\'alez-L\'opez and Najoung Kim
\item The diversity and inclusion chairs Ziyu Yao, Gemma Bel Enguix and Maria Pacheco
\item The sponsorship chairs Ivan Meza and Mohit Iyyer
\item The student volunteers chairs Lucy Lu Wang and Liang Huang
\item The ethics chairs Cissi Alm, Diana Galvan Sosa, Anjalie Field, Ameeta Agrawal, Daniel Fried, Mark Yatskar, Maria Antoniak, and Alane Suhr
\item The handbook chair Luke Gessler
\item The reproducibility chairs Ghazaleh Kazeminejad, Koustuv Sinha, Peter Jansen, Pastor Lopez, and Ian Magnusson
\item The best paper committee chairs Isabelle Augenstein and Manuel Montes-y-G\'omez
\item The local chair Hiram Calvo
\end{itemize}

Many thanks also to the chairs of the previous year's conferences, who were always ready to help and share their experience, and to the members of the ACL and NAACL Executive Committees for their support, feedback and advice, especially Iryna Gurevych, Emily Bender, and Graham Neubig. 

Finally, I would like to thank all authors, invited speakers and panelists, area chairs and reviewers, the volunteers organizing and chairing sessions, and all attendees, in-person and virtual. Thank you for helping us make NAACL 2024 come to life.

Welcome and hope you all enjoy the conference!

\vspace{1em}

Katrin Erk\\
The University of Texas at Austin\\
NAACL-2024 General Chair
